Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-04 paper_jasa.tex
data summary

>>>>

{\bf Cleaning data:} There are five suggested approach to clean the data. They are

\begin{enumerate}
\item not throw out anything
\item throw out people where we don't have demographic information
\item throw out all people with 0 percent correct
\item only include people with at least 20 percent correct (current suggestion)
\item include people with 50\% on all easy lineups (as suggested before)
\end{enumerate}

\begin{table}[hbtp]
\caption{Summary of unique subjects and their total feedbacks after applying five screening process on all three experimental data}
\begin{center}
\begin{tabular}{rrrrr|rrrr|rrrr}
  \hline
Screening &  \multicolumn{4}{c} {Experiment 1}  & \multicolumn{4}{c} {Experiment 2}  & \multicolumn{4}{c} {Experiment 3} \\
 \cline{2-5}  \cline{6-9}   \cline{10-13}
criteria & total & male & female & feedbacks & total & male & female & feedbacks & total & male & female & feedbacks \\ 
  \hline
1 & 520 & 264 & 201 & 4914 & 520 & 264 & 201 & 4914 & 520 & 264 & 201 & 4914 \\ 
  2 & 465 & 264 & 201 & 4624 & 465 & 264 & 201 & 4624 & 465 & 264 & 201 & 4624 \\ 
  3 & 384 & 200 & 165 & 4187 & 384 & 200 & 165 & 4187 & 384 & 200 & 165 & 4187 \\ 
  4 & 318 & 168 & 135 & 3395 & 318 & 168 & 135 & 3395 & 318 & 168 & 135 & 3395 \\ 
  5 & 277 & 139 & 124 & 3008 & 277 & 139 & 124 & 3008 & 277 & 139 & 124 & 3008 \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:summary}
\end{table}
